Guarded Recursive Type Theory via Sized Types

### 2019-01-07 code-oneclock-paper/latex/paper.tex
a bit of work on the paper on the plane
Fixed lipics and agda to latex

\documentclass{amsart}

@@

@@

\DeclareUnicodeCharacter{915}{$\Gamma$}
\DeclareUnicodeCharacter{931}{$\Sigma$}
\DeclareUnicodeCharacter{948}{$\delta$}
\DeclareUnicodeCharacter{957}{$\nu$}
\DeclareUnicodeCharacter{8718}{$\blacksquare$}
\DeclareUnicodeCharacter{8759}{::}
\DeclareUnicodeCharacter{9659}{$\vartriangleright$}

@@

@@

\section{Presheaves}

A presheaf is a functor from the category of sizes to \D{Set}.

@@

Presheaves are the objects of a category whose morphisms are natural
transformations. This is a cartesian closed category with finite
coproducts.
The terminal object is the constant presheaf on the unit type \D{⊤},
i.e. \D{Terminal} = \D{Const ⊤}. Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Prod} \Ar{P} \Ar{Q} for their cartesian
product. The action of \D{Prod} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\input{Presheaves/Product}
%\Fi{PSh.Obj} \Ar{P i ×} \Fi{PSh.Obj} \Ar{Q i}.
Coproducts are also defined in a similar pointwise way.

Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Exp} \Ar{P} \Ar{Q} for their exponential. 
 The action of \D{Exp} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\input{Presheaves/Exp}

\section{The Model}

\subsection{Types, Contexts, Terms}

A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
is a preasheaf in \D{PSh}.

@@

\subsection{Operations on Contexts}

\subsection{Substitution}

>>>>

\documentclass[a4paper,UKenglish,cleveref, autoref,numberwithinsect]{lipics-v2018}

@@

\usepackage{newunicodechar}

@@

\newunicodechar{⊤}{$\top$}
\newunicodechar{≡}{$\equiv$}
\newunicodechar{₁}{$_1$}
\newunicodechar{Γ}{$\Gamma$}
\newunicodechar{Σ}{$\Sigma$}
\newunicodechar{λ}{$\lambda$}
\newunicodechar{∙}{$\cdot$}

@@

\newcommand{\remove}[1]{}

@@

\section{Presheaves}
A presheaf is a functor from the category of sizes to \D{Set}.

@@

Presheaves are the objects of a category whose morphisms are natural
transformations. This is a cartesian closed category with finite
coproducts.
The terminal object is the constant presheaf on the unit type \D{⊤},
i.e. \D{Terminal} = \D{Const ⊤}. Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Prod} \Ar{P} \Ar{Q} for their cartesian
product. The action of \D{Prod} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\remove{
\input{Presheaves/Product}
%\Fi{PSh.Obj} \Ar{P i ×} \Fi{PSh.Obj} \Ar{Q i}.
Coproducts are also defined in a similar pointwise way.

Given two presheaves \Ar{P} and
\Ar{Q}, we write \D{Exp} \Ar{P} \Ar{Q} for their exponential. 
 The action of \D{Exp} \Ar{P} \Ar{Q} on a size \Ar{i} is
defined as follows:
\input{Presheaves/Exp}
}
\section{The Model}

\subsection{Types, Contexts, Terms}
A context in \IC{set} is an element of \D{Set}. A context in \IC{tot}
is a preasheaf in \D{PSh}.

@@

We write \D{∙} for the empty context and \Ar{Γ} \D{,,} \Ar{A} for the
extension of the context \Ar{Γ} with the type \Ar{A}. We have
the usual variable, weakening and substitutution operations.
%\subsection{Operations on Contexts}
%\subsection{Substitution}
